%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Software Engineer II} % Job title
{Google} % Organization
{Bengaluru, IN} % Location
{Aug. 2020 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Build high impacting 1P sports features on Google Search and Assistant.}
\item {Lead a team of 5 Eng. for FIFA World Cup 2022 related efforts on Discover.}
\item {Pioneered first sports UGC feature on Google search. This further opened doors for more UGC efforts on Google Search.}
\item {Lead a team of 10 Eng. to drive Code Quality improvement effort of enitre Search Vertical codebase.}
\item {Developed multiple features and did quality/ranking enhancement for the Paralympics, and Summer and Winter Olympics. Nearly 2.8 billion impresions on search and 5.2 million impressions on assistant.}
\item {Enhanced user experience for popular sports events on search and assistant by giving detailed context about the event. This led to 0.6 million impression increase for superbowl.}
\item {Improved the reliability of understanding user intent for various sports event. Improved triggering by \~13\% for superbowl.}
\item {Contributed to Google CodeJam and Kickstart by volunteering for various Eng tasks.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Development Engineer Intern} % Job title
{Amazon} % Organization
{Bengaluru, IN} % Location
{Jan. 2020 - July, 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Created a Version Diff feature on FCStowportal Rule Engine.}
\item {Creating HTTPS endpoint on production pipeline of AFTMoveApp for externalising it.}
\item {Threat-model analysis of Case-Stow for Anvil security certification.}
\item {Prevented Predicant App from outage due to excessive retries.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}