%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Service Oriented Architecture | ASP.NET | WCF Services} % Role
{Semi-Automated Code Testing Environment} % Event
{Nadiad,IN} % Location
{Jan.2018 - March.2019} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {A tool that performs unit testing for standalone code or functions.}
\item {This tool is completely based on Service Oriented Architecture and is designed with utmost loose coupling.}
\item {This tools works on time based threshold and continuously checks the output of absolutely correct code and code that is being tested.}
\item {The back-end Services can be consumed platform independently hence incorporating reusability and extensibility.}
\item {Follows all the SOA principles.}
\item {Further Extension to project can include development in the field of code synthesis, or using data analytics to make test generation more intelligent instead of probabilistic.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Angular 6 | Node.JS with Express Framework | Mongodb} % Role
{Stalkbook (A Website that Stalks Coders Profile from various Platform)} % Event
{Nadiad,IN} % Location
{Jul.2018 - Oct.2018} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {Scrapped Profiles of registered coders from various platform using their coding handle.}
\item {Used 'Puppeteer' and 'Cheerio' Library of Node.Js for scrapping.}
\item {Fully responsive front-end using Angular 6}
\item {Whole Scrapping Logic is backend 'API' using RESTful services}
\end{cvitems}
}

%------------------------------------------------

\cventry
{ASP.NET | MVC Application | EntityFramework} % Role
{Employee Professional Activity Management System (EPAMS)} % Event
{Nadiad, IN} % Location
{Sept.2018 - Oct.2018} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {A portal for smooth interaction between HR Dept. and Employees of the Firm.}
\item {Employees submit any new project or research they undertook or any workshop they attended etc with proof and HR personnel varifies and approves it.}
\item {This solves a problem of authenticity of information in person's CV. Any firm can verify the Employees CV from their past Employer using this portal.}
\item {This is an MVC application using EntityFramework(ORM Code First Approach).}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Python and Django Framework} % Role
{An Airline Management System} % Event
{Nadiad, IN} % Location
{Jan.2018 - Apr.2018} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {A portal to facilitate Regular operation of an Airline Company.}
\item {Deals with basic CRUD operation related to Adding/Updating Flights, Changing their Routes and their Live Status.}
\item {A first hand Experience at making Website. The website provides very basic Functionality.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}